\lettersection{Why Me?}
\iftoggle{isSoft}{%
    % SOFTWARE/SYSTEMS STORY
    At Clutterbot, I led the transition to a Debian-based deployment system. By treating infrastructure as code, I reduced fleet update cycles from a week of manual effort to a two-hour automated process. This taught me how to manage 100\% parity across global deployments—a skill directly applicable to maintaining rigorous version control at \companyName.
}{%
    % HARDWARE/MECH/ELEC STORY
    At Clutterbot, I identified critical failure points in legacy actuator designs that were stalling production. By designing bespoke assembly jigs and refining mechanical tolerances, I stabilized our manufacturing output and ensured hardware-in-the-loop validation for every unit leaving the bench.
}

\vspace{2mm} % Slight breathing room

This experience aligns with your need for \textbf{\targetPainPoint}. In my current role, I lead end-to-end Quality Assurance across both mechanical and software stacks. Most recently, I designed and operated \textbf{HALT (Highly Accelerated Lifecycle Testing)} rigs for actuators and gearboxes. This wasn't just about finding faults; it was about using those insights in SolidWorks to redesign components for long-term reliability.

I am comfortable bridging the gap between a prototype and high-volume production. Whether it is investigating field issues or supporting your \textbf{ISO 13485} requirements through \textbf{\bonusSkill}, I focus on clearing technical roadblocks so the team can scale without compromising quality.
