\cvsection{Relevant Projects}
\begin{cventries}
  \cventry%
    {Lead Engineer \& Team Captain}
    {VEX \& VEXU Robotics Competition}
    {Global / New Zealand}
    {2016 --- 2024}
    {
      \begin{cvitems}
        \item {Led design, fabrication, and programming for the \textbf{2023 VEXU World Championship Excellence Award} winning team.}
        \showfor{isMech}{
          \item {Manufactured high-precision robot chassis from sheet aluminium using CNC routers and custom 3D-printed components.}
        }
        \ifboolexpr{togl {isSoft} or togl {isEmbed}}{
          \item {Developed custom motion control algorithms and sensor fusion for autonomous navigation for single robot and 2vs2 match formats.}
        }{}
        \item {Managed the team and processes including CAD version control and \textbf{hardware-in-the-loop testing cycles}.}
      \end{cvitems}
    }
  \showfor{isMech}{
    \cventry%
      {Contract Fabricator}
      {Custom Air Intake Adaptor}
      {Personal Commission}
      {2024}
      {
        \begin{cvitems}
          \item {Engineered a bespoke 6061-T6 aluminium interface block to adapt a performance engine to an existing intake manifold.}
          \item {Completed measurements, SolidWorks design, \textbf{HSMWorks CAM pathing}, and \textbf{3-axis CNC machining.}}
        \end{cvitems}
      }
  }
\cventry%
    {Electronics \& HV Systems --- Wiring Harness Developer}
    {Formula SAE --- University of Auckland Racing}
    {Wellington / Auckland, NZ}
    {2022 --- 2023}
    {
      \begin{cvitems}
        \item {Contributed to the \textbf{2022 Australasian Championship} winning vehicle as part of the electronics and high-voltage team.}
        \item {Designed and built the vehicle wiring harness using \textbf{Autodesk Inventor}; led the team's transition from a monolithic harness to a \textbf{modular architecture with breakout boxes}, separating systems to improve fault isolation and development cycle speed.}
        \item {Advocated for and implemented the modular redesign following a short-circuit failure that invalidated the entire previous harness — the new architecture eliminated that class of failure and reduced harness rework time significantly.}
        \showfor{isMech}{
          \item {Managed mechanical routing, mounting, and connector selection across high and low voltage domains, adhering to strict FSAE electrical safety regulations.}
        }
        \showfor{isElec}{
          \item {Performed HV segment assembly, grounding architecture, and system-level electrical validation against FSAE safety standards.}
        }
      \end{cvitems}
    }
  \cventry%
    {Designer \& Builder}
    {Self-Built 3-Axis CNC Router}
    {Personal Project}
    {2022 --- 2023}
    {
      \begin{cvitems}
        \item {Constructed a 0.1mm precision 3-axis CNC router capable of machining 6061-T6 aluminium for VEXU and personal clients.}
        \showfor{isMech}{
          \item {Integrated a 2.2kW water-cooled spindle and managed the mechanical alignment of the $970 \times 610$mm work area.}
        }
        \showfor{isSoft}{
          \item {Configured GRBL-based control systems and optimised CAM toolpaths for efficient material removal and surface finish.}
        }
      \end{cvitems}
    }
\end{cventries}
